The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-03-18 Paper.Rmd
thinkig about Discussion

We showed that non-N copula structure and asymmetric tail dependence are 
exceedingly common in datasets that range across multiple sub-disciplines
of ecology. Via basic mathematical models, we hypothesized two probable
mechanisms causing those non-N copula structures with asymmetric tail-dependence. One
mechanism was "Moran"-like effect where dependence structure between ecological
variables from two locations was shaped by the dependence structure of 
the environmental variables at those patches. Second mechanism, a mimic of 
Liebig's law of the minimum, explored
the asymmetric influence of environmental variables which 
could limit the growth of populations when below (or beyond)
a certain threshold. Using model simulations and real ecological data,
we concluded asymmetric tail dependence feature of 
non-N copula could affect (1) the skewness (henceforth, the stability)
of spatially averaged quantities over years, (2) the extinction risk 
and (3) the spatial Taylor's law slope of metapopulations.

>>>>

<!--what we did and why is it important to study?-->
We showed that non-N copula structure and asymmetric tail dependence are 
exceedingly common in datasets that range across multiple sub-disciplines
of ecology. Via basic mathematical models, we hypothesized two probable
mechanisms causing those non-N copula structures with asymmetric tail-dependence. One
mechanism was "Moran"-like effect where dependence structure between ecological
variables from two locations was shaped by the dependence structure of 
the environmental variables at those patches. Second mechanism, a mimic of 
Liebig's law of the minimum, explored
the asymmetric influence of environmental variables which 
could limit the growth of populations when below (or beyond)
a certain threshold. Using model simulations and real ecological data,
we concluded asymmetric tail dependence feature of 
non-N copula could affect (1) the skewness (henceforth, the stability)
of spatially averaged quantities over years, (2) the extinction risk 
and (3) the spatial Taylor's law slope of metapopulations.
